---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sdr.neuronal

<!-- badges: start -->
<!-- badges: end -->

The sdr.neuronal package was created by Sideridis Vasileios during his work on the neuronsXnets project. Contains useful functions for loading, processing and plotting data related with the aforementioned project. 

## Installation

You will be able to install the released version of sdr.neuronal from [CRAN](https://CRAN.R-project.org) soon with:

``` r
install.packages("sdr.neuronal")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("vsideridis/sdr.neuronal")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(sdr.neuronal)
## basic example code
```

